---
title: "DATA 205 ABS Data Cleaning and EDA"
author: "Emilio Difilippantonio"
date: "2025-04-07"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
```


```{r}
# Loading in the data set
high <- read_csv("ABS_High_Volume_Weekly.csv")
mid <- read_csv("ABS_Medium_Volume_Weekly.csv")
low <- read_csv("ABS_Low_Volume_Weekly.csv")
```

```{r}
# Renaming the columns
colnames(high) <- c("item_id", "description", "bottles_per_case", "cost_per_bottle", "week_1", "week_2", "week_3", "week_4", "week_5", "week_6", "week_7", "week_8", "week_9", "week_10", "week_11", "week_12", "week_13", "week_14", "week_15", "week_16", "week_17", "week_18", "week_19", "week_20", "week_21", "week_22", "week_23", "week_24", "week_25", "week_26", "week_27", "week_28", "week_29", "week_30", "week_31", "week_32", "week_33", "week_34", "week_35", "week_36",  "week_37", "week_38", "week_39", "week_40", "week_41", "week_42", "week_43", "week_44", "week_45", "week_46", "week_47", "week_48", "week_49", "week_50", "week_51", "week_52", "week_53", "total")

colnames(mid) <- c("item_id", "description", "bottles_per_case", "cost_per_bottle", "week_1", "week_2", "week_3", "week_4", "week_5", "week_6", "week_7", "week_8", "week_9", "week_10", "week_11", "week_12", "week_13", "week_14", "week_15", "week_16", "week_17", "week_18", "week_19", "week_20", "week_21", "week_22", "week_23", "week_24", "week_25", "week_26", "week_27", "week_28", "week_29", "week_30", "week_31", "week_32", "week_33", "week_34", "week_35", "week_36",  "week_37", "week_38", "week_39", "week_40", "week_41", "week_42", "week_43", "week_44", "week_45", "week_46", "week_47", "week_48", "week_49", "week_50", "week_51", "week_52", "week_53", "total")

colnames(low) <- c("item_id", "description", "bottles_per_case", "cost_per_bottle", "week_1", "week_2", "week_3", "week_4", "week_5", "week_6", "week_7", "week_8", "week_9", "week_10", "week_11", "week_12", "week_13", "week_14", "week_15", "week_16", "week_17", "week_18", "week_19", "week_20", "week_21", "week_22", "week_23", "week_24", "week_25", "week_26", "week_27", "week_28", "week_29", "week_30", "week_31", "week_32", "week_33", "week_34", "week_35", "week_36",  "week_37", "week_38", "week_39", "week_40", "week_41", "week_42", "week_43", "week_44", "week_45", "week_46", "week_47", "week_48", "week_49", "week_50", "week_51", "week_52", "week_53", "total")
```

```{r}
# Creating new datasets where the sales are in cases, not bottles
highCase <- mutate(high, week_1 = week_1 / bottles_per_case)
highCase <- mutate(highCase, week_2 = week_2 / bottles_per_case)
highCase <- mutate(highCase, week_3 = week_3 / bottles_per_case)
highCase <- mutate(highCase, week_4 = week_4 / bottles_per_case)
highCase <- mutate(highCase, week_5 = week_5 / bottles_per_case)
highCase <- mutate(highCase, week_6 = week_6 / bottles_per_case)
highCase <- mutate(highCase, week_7 = week_7 / bottles_per_case)
highCase <- mutate(highCase, week_8 = week_8 / bottles_per_case)
highCase <- mutate(highCase, week_9 = week_9 / bottles_per_case)
highCase <- mutate(highCase, week_10 = week_10 / bottles_per_case)
highCase <- mutate(highCase, week_11 = week_11 / bottles_per_case)
highCase <- mutate(highCase, week_12 = week_12 / bottles_per_case)
highCase <- mutate(highCase, week_13 = week_13 / bottles_per_case)
highCase <- mutate(highCase, week_14 = week_14 / bottles_per_case)
highCase <- mutate(highCase, week_15 = week_15 / bottles_per_case)
highCase <- mutate(highCase, week_16 = week_16 / bottles_per_case)
highCase <- mutate(highCase, week_17 = week_17 / bottles_per_case)
highCase <- mutate(highCase, week_18 = week_18 / bottles_per_case)
highCase <- mutate(highCase, week_19 = week_19 / bottles_per_case)
highCase <- mutate(highCase, week_20 = week_20 / bottles_per_case)
highCase <- mutate(highCase, week_21 = week_21 / bottles_per_case)
highCase <- mutate(highCase, week_22 = week_22 / bottles_per_case)
highCase <- mutate(highCase, week_23 = week_23 / bottles_per_case)
highCase <- mutate(highCase, week_24 = week_24 / bottles_per_case)
highCase <- mutate(highCase, week_25 = week_25 / bottles_per_case)
highCase <- mutate(highCase, week_26 = week_26 / bottles_per_case)
highCase <- mutate(highCase, week_27 = week_27 / bottles_per_case)
highCase <- mutate(highCase, week_28 = week_28 / bottles_per_case)
highCase <- mutate(highCase, week_29 = week_29 / bottles_per_case)
highCase <- mutate(highCase, week_30 = week_30 / bottles_per_case)
highCase <- mutate(highCase, week_31 = week_31 / bottles_per_case)
highCase <- mutate(highCase, week_32 = week_32 / bottles_per_case)
highCase <- mutate(highCase, week_33 = week_33 / bottles_per_case)
highCase <- mutate(highCase, week_34 = week_34 / bottles_per_case)
highCase <- mutate(highCase, week_35 = week_35 / bottles_per_case)
highCase <- mutate(highCase, week_36 = week_36 / bottles_per_case)
highCase <- mutate(highCase, week_37 = week_37 / bottles_per_case)
highCase <- mutate(highCase, week_38 = week_38 / bottles_per_case)
highCase <- mutate(highCase, week_39 = week_39 / bottles_per_case)
highCase <- mutate(highCase, week_40 = week_40 / bottles_per_case)
highCase <- mutate(highCase, week_41 = week_41 / bottles_per_case)
highCase <- mutate(highCase, week_42 = week_42 / bottles_per_case)
highCase <- mutate(highCase, week_43 = week_43 / bottles_per_case)
highCase <- mutate(highCase, week_44 = week_44 / bottles_per_case)
highCase <- mutate(highCase, week_45 = week_45 / bottles_per_case)
highCase <- mutate(highCase, week_46 = week_46 / bottles_per_case)
highCase <- mutate(highCase, week_47 = week_47 / bottles_per_case)
highCase <- mutate(highCase, week_48 = week_48 / bottles_per_case)
highCase <- mutate(highCase, week_49 = week_49 / bottles_per_case)
highCase <- mutate(highCase, week_50 = week_50 / bottles_per_case)
highCase <- mutate(highCase, week_51 = week_51 / bottles_per_case)
highCase <- mutate(highCase, week_52 = week_52 / bottles_per_case)
highCase <- mutate(highCase, week_52 = week_52 / bottles_per_case)
highCase <- mutate(lowCase, week_53 = week_53 / bottles_per_case)
highCase <- mutate(highCase, total = total / bottles_per_case)

midCase <- mutate(mid, week_1 = week_1 / bottles_per_case)
midCase <- mutate(midCase, week_2 = week_2 / bottles_per_case)
midCase <- mutate(midCase, week_3 = week_3 / bottles_per_case)
midCase <- mutate(midCase, week_4 = week_4 / bottles_per_case)
midCase <- mutate(midCase, week_5 = week_5 / bottles_per_case)
midCase <- mutate(midCase, week_6 = week_6 / bottles_per_case)
midCase <- mutate(midCase, week_7 = week_7 / bottles_per_case)
midCase <- mutate(midCase, week_8 = week_8 / bottles_per_case)
midCase <- mutate(midCase, week_9 = week_9 / bottles_per_case)
midCase <- mutate(midCase, week_10 = week_10 / bottles_per_case)
midCase <- mutate(midCase, week_11 = week_11 / bottles_per_case)
midCase <- mutate(midCase, week_12 = week_12 / bottles_per_case)
midCase <- mutate(midCase, week_13 = week_13 / bottles_per_case)
midCase <- mutate(midCase, week_14 = week_14 / bottles_per_case)
midCase <- mutate(midCase, week_15 = week_15 / bottles_per_case)
midCase <- mutate(midCase, week_16 = week_16 / bottles_per_case)
midCase <- mutate(midCase, week_17 = week_17 / bottles_per_case)
midCase <- mutate(midCase, week_18 = week_18 / bottles_per_case)
midCase <- mutate(midCase, week_19 = week_19 / bottles_per_case)
midCase <- mutate(midCase, week_20 = week_20 / bottles_per_case)
midCase <- mutate(midCase, week_21 = week_21 / bottles_per_case)
midCase <- mutate(midCase, week_22 = week_22 / bottles_per_case)
midCase <- mutate(midCase, week_23 = week_23 / bottles_per_case)
midCase <- mutate(midCase, week_24 = week_24 / bottles_per_case)
midCase <- mutate(midCase, week_25 = week_25 / bottles_per_case)
midCase <- mutate(midCase, week_26 = week_26 / bottles_per_case)
midCase <- mutate(midCase, week_27 = week_27 / bottles_per_case)
midCase <- mutate(midCase, week_28 = week_28 / bottles_per_case)
midCase <- mutate(midCase, week_29 = week_29 / bottles_per_case)
midCase <- mutate(midCase, week_30 = week_30 / bottles_per_case)
midCase <- mutate(midCase, week_31 = week_31 / bottles_per_case)
midCase <- mutate(midCase, week_32 = week_32 / bottles_per_case)
midCase <- mutate(midCase, week_33 = week_33 / bottles_per_case)
midCase <- mutate(midCase, week_34 = week_34 / bottles_per_case)
midCase <- mutate(midCase, week_35 = week_35 / bottles_per_case)
midCase <- mutate(midCase, week_36 = week_36 / bottles_per_case)
midCase <- mutate(midCase, week_37 = week_37 / bottles_per_case)
midCase <- mutate(midCase, week_38 = week_38 / bottles_per_case)
midCase <- mutate(midCase, week_39 = week_39 / bottles_per_case)
midCase <- mutate(midCase, week_40 = week_40 / bottles_per_case)
midCase <- mutate(midCase, week_41 = week_41 / bottles_per_case)
midCase <- mutate(midCase, week_42 = week_42 / bottles_per_case)
midCase <- mutate(midCase, week_43 = week_43 / bottles_per_case)
midCase <- mutate(midCase, week_44 = week_44 / bottles_per_case)
midCase <- mutate(midCase, week_45 = week_45 / bottles_per_case)
midCase <- mutate(midCase, week_46 = week_46 / bottles_per_case)
midCase <- mutate(midCase, week_47 = week_47 / bottles_per_case)
midCase <- mutate(midCase, week_48 = week_48 / bottles_per_case)
midCase <- mutate(midCase, week_49 = week_49 / bottles_per_case)
midCase <- mutate(midCase, week_50 = week_50 / bottles_per_case)
midCase <- mutate(midCase, week_51 = week_51 / bottles_per_case)
midCase <- mutate(midCase, week_52 = week_52 / bottles_per_case)
midCase <- mutate(midCase, week_52 = week_52 / bottles_per_case)
midCase <- mutate(lowCase, week_53 = week_53 / bottles_per_case)
midCase <- mutate(midCase, total = total / bottles_per_case)

lowCase <- mutate(low, week_1 = week_1 / bottles_per_case)
lowCase <- mutate(lowCase, week_2 = week_2 / bottles_per_case)
lowCase <- mutate(lowCase, week_3 = week_3 / bottles_per_case)
lowCase <- mutate(lowCase, week_4 = week_4 / bottles_per_case)
lowCase <- mutate(lowCase, week_5 = week_5 / bottles_per_case)
lowCase <- mutate(lowCase, week_6 = week_6 / bottles_per_case)
lowCase <- mutate(lowCase, week_7 = week_7 / bottles_per_case)
lowCase <- mutate(lowCase, week_8 = week_8 / bottles_per_case)
lowCase <- mutate(lowCase, week_9 = week_9 / bottles_per_case)
lowCase <- mutate(lowCase, week_10 = week_10 / bottles_per_case)
lowCase <- mutate(lowCase, week_11 = week_11 / bottles_per_case)
lowCase <- mutate(lowCase, week_12 = week_12 / bottles_per_case)
lowCase <- mutate(lowCase, week_13 = week_13 / bottles_per_case)
lowCase <- mutate(lowCase, week_14 = week_14 / bottles_per_case)
lowCase <- mutate(lowCase, week_15 = week_15 / bottles_per_case)
lowCase <- mutate(lowCase, week_16 = week_16 / bottles_per_case)
lowCase <- mutate(lowCase, week_17 = week_17 / bottles_per_case)
lowCase <- mutate(lowCase, week_18 = week_18 / bottles_per_case)
lowCase <- mutate(lowCase, week_19 = week_19 / bottles_per_case)
lowCase <- mutate(lowCase, week_20 = week_20 / bottles_per_case)
lowCase <- mutate(lowCase, week_21 = week_21 / bottles_per_case)
lowCase <- mutate(lowCase, week_22 = week_22 / bottles_per_case)
lowCase <- mutate(lowCase, week_23 = week_23 / bottles_per_case)
lowCase <- mutate(lowCase, week_24 = week_24 / bottles_per_case)
lowCase <- mutate(lowCase, week_25 = week_25 / bottles_per_case)
lowCase <- mutate(lowCase, week_26 = week_26 / bottles_per_case)
lowCase <- mutate(lowCase, week_27 = week_27 / bottles_per_case)
lowCase <- mutate(lowCase, week_28 = week_28 / bottles_per_case)
lowCase <- mutate(lowCase, week_29 = week_29 / bottles_per_case)
lowCase <- mutate(lowCase, week_30 = week_30 / bottles_per_case)
lowCase <- mutate(lowCase, week_31 = week_31 / bottles_per_case)
lowCase <- mutate(lowCase, week_32 = week_32 / bottles_per_case)
lowCase <- mutate(lowCase, week_33 = week_33 / bottles_per_case)
lowCase <- mutate(lowCase, week_34 = week_34 / bottles_per_case)
lowCase <- mutate(lowCase, week_35 = week_35 / bottles_per_case)
lowCase <- mutate(lowCase, week_36 = week_36 / bottles_per_case)
lowCase <- mutate(lowCase, week_37 = week_37 / bottles_per_case)
lowCase <- mutate(lowCase, week_38 = week_38 / bottles_per_case)
lowCase <- mutate(lowCase, week_39 = week_39 / bottles_per_case)
lowCase <- mutate(lowCase, week_40 = week_40 / bottles_per_case)
lowCase <- mutate(lowCase, week_41 = week_41 / bottles_per_case)
lowCase <- mutate(lowCase, week_42 = week_42 / bottles_per_case)
lowCase <- mutate(lowCase, week_43 = week_43 / bottles_per_case)
lowCase <- mutate(lowCase, week_44 = week_44 / bottles_per_case)
lowCase <- mutate(lowCase, week_45 = week_45 / bottles_per_case)
lowCase <- mutate(lowCase, week_46 = week_46 / bottles_per_case)
lowCase <- mutate(lowCase, week_47 = week_47 / bottles_per_case)
lowCase <- mutate(lowCase, week_48 = week_48 / bottles_per_case)
lowCase <- mutate(lowCase, week_49 = week_49 / bottles_per_case)
lowCase <- mutate(lowCase, week_50 = week_50 / bottles_per_case)
lowCase <- mutate(lowCase, week_51 = week_51 / bottles_per_case)
lowCase <- mutate(lowCase, week_52 = week_52 / bottles_per_case)
lowCase <- mutate(lowCase, week_52 = week_52 / bottles_per_case)
lowCase <- mutate(lowCase, week_53 = week_53 / bottles_per_case)
lowCase <- mutate(lowCase, total = total / bottles_per_case)
```

```{r}
# Adding a variable to indicate store volume (it's redundant in these data set, but when I combine them, it will be useful)
highCase <- mutate(highCase, volume = "high")
midCase <- mutate(midCase, volume = "medium")
lowCase <- mutate(lowCase, volume = "low")
```


```{r}
# Combining all of the data sets
bound <- bind_rows(highCase, midCase, lowCase)

# Making volume a factor and setting the levels
bound$volume <- as_factor(bound$volume)
levels(bound$volume) <- c("high", "medium", "low")
```


The cleaning is finished. Time for EDA.

```{r}
# Plotting total sales of each item across all stores
ggplot(bound, aes(y = total)) +
  geom_boxplot()
```
As we can see, there are many outliers, making it difficult to view and understand the data. Let's remove them and remake the visualization.

```{r}
# Creating the data set without outliers
bound_noOut <- filter(bound, total <= 25)

# Remaking the visualization
ggplot(bound_noOut, aes(y = total)) +
  geom_boxplot()
```

This graph is much easier to read and tells us that the median number of cases sold of a product in 2024 is about 1, with a heavy rightwards skew that includes some heavy outliers (the ones seen in the previous visualization).

Let's break this data down.

```{r}
# Making a histgram showing sales from each store
ggplot(bound_noOut, aes(total)) +
  geom_histogram() +
  facet_wrap(vars(bound_noOut$volume), scales = "free_y") +
  labs(
    title = "Frequency of total sales in cases of product in 2024 by store volume",
    x = "Store Sales Volume",
    y = "Frequency"
  )
```

Clearly, something is wrong. I have looked over my code several times but cannot find the mistake.

```{r}
# Creating new data sets for sales in each week
week1 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_1, volume)
week1 <- mutate(week1, week = 1)
week1 <- week1 |> rename(sales = week_1)

week2 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_2, volume)
week2 <- mutate(week2, week = 2)
week2 <- week2 |> rename(sales = week_2)

week3 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_3, volume)
week3 <- mutate(week3, week = 3)
week3 <- week3 |> rename(sales = week_3)

week4 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_4, volume)
week4 <- mutate(week4, week = 4)
week4 <- week4 |> rename(sales = week_4)

week5 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_5, volume)
week5 <- mutate(week5, week = 5)
week5 <- week5 |> rename(sales = week_5)

week6 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_6, volume)
week6 <- mutate(week6, week = 6)
week6 <- week6 |> rename(sales = week_6)

week7 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_7, volume)
week7 <- mutate(week7, week = 7)
week7 <- week7 |> rename(sales = week_7)

week8 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_8, volume)
week8 <- mutate(week8, week = 8)
week8 <- week8 |> rename(sales = week_8)

week9 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_9, volume)
week9 <- mutate(week9, week = 9)
week9 <- week9 |> rename(sales = week_9)

week10 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_10, volume)
week10 <- mutate(week10, week = 10)
week10 <- week10 |> rename(sales = week_10)

week11 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_11, volume)
week11 <- mutate(week11, week = 11)
week11 <- week11 |> rename(sales = week_11)

week12 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_12, volume)
week12 <- mutate(week12, week = 12)
week12 <- week12 |> rename(sales = week_12)

week13 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_13, volume)
week13 <- mutate(week13, week = 13)
week13 <- week13 |> rename(sales = week_13)

week14 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_14, volume)
week14 <- mutate(week14, week = 14)
week14 <- week14 |> rename(sales = week_14)

week15 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_15, volume)
week15 <- mutate(week15, week = 15)
week15 <- week15 |> rename(sales = week_15)

week16 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_16, volume)
week16 <- mutate(week16, week = 16)
week16 <- week16 |> rename(sales = week_16)

week17 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_17, volume)
week17 <- mutate(week17, week = 17)
week17 <- week17 |> rename(sales = week_17)

week18 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_18, volume)
week18 <- mutate(week18, week = 18)
week18 <- week18 |> rename(sales = week_18)

week19 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_19, volume)
week19 <- mutate(week19, week = 19)
week19 <- week19 |> rename(sales = week_19)

week20 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_20, volume)
week20 <- mutate(week20, week = 20)
week20 <- week20 |> rename(sales = week_20)

week21 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_21, volume)
week21 <- mutate(week21, week = 21)
week21 <- week21 |> rename(sales = week_21)

week22 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_22, volume)
week22 <- mutate(week22, week = 22)
week22 <- week22 |> rename(sales = week_22)

week23 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_23, volume)
week23 <- mutate(week23, week = 23)
week23 <- week23 |> rename(sales = week_23)

week24 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_24, volume)
week24 <- mutate(week24, week = 24)
week24 <- week24 |> rename(sales = week_24)

week25 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_25, volume)
week25 <- mutate(week25, week = 25)
week25 <- week25 |> rename(sales = week_25)

week26 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_26, volume)
week26 <- mutate(week26, week = 26)
week26 <- week26 |> rename(sales = week_26)

week27 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_27, volume)
week27 <- mutate(week27, week = 27)
week27 <- week27 |> rename(sales = week_27)

week28 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_28, volume)
week28 <- mutate(week28, week = 28)
week28 <- week28 |> rename(sales = week_28)

week29 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_29, volume)
week29 <- mutate(week29, week = 29)
week29 <- week29 |> rename(sales = week_29)

week30 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_30, volume)
week30 <- mutate(week30, week = 30)
week30 <- week30 |> rename(sales = week_30)

week31 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_31, volume)
week31 <- mutate(week31, week = 31)
week31 <- week31 |> rename(sales = week_31)

week32 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_32, volume)
week32 <- mutate(week32, week = 32)
week32 <- week32 |> rename(sales = week_32)

week33 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_33, volume)
week33 <- mutate(week33, week = 33)
week33 <- week33 |> rename(sales = week_33)

week34 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_34, volume)
week34 <- mutate(week34, week = 34)
week34 <- week34 |> rename(sales = week_34)

week35 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_35, volume)
week35 <- mutate(week35, week = 35)
week35 <- week35 |> rename(sales = week_35)

week36 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_36, volume)
week36 <- mutate(week36, week = 36)
week36 <- week36 |> rename(sales = week_36)

week37 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_37, volume)
week37 <- mutate(week37, week = 37)
week37 <- week37 |> rename(sales = week_37)

week38 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_38, volume)
week38 <- mutate(week38, week = 38)
week38 <- week38 |> rename(sales = week_38)

week39 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_39, volume)
week39 <- mutate(week39, week = 39)
week39 <- week39 |> rename(sales = week_39)

week40 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_40, volume)
week40 <- mutate(week40, week = 40)
week40 <- week40 |> rename(sales = week_40)

week41 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_41, volume)
week41 <- mutate(week41, week = 41)
week41 <- week41 |> rename(sales = week_41)

week42 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_42, volume)
week42 <- mutate(week42, week = 42)
week42 <- week42 |> rename(sales = week_42)

week43 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_43, volume)
week43 <- mutate(week43, week = 43)
week43 <- week43 |> rename(sales = week_43)

week44 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_44, volume)
week44 <- mutate(week44, week = 44)
week44 <- week44 |> rename(sales = week_44)

week45 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_45, volume)
week45 <- mutate(week45, week = 45)
week45 <- week45 |> rename(sales = week_45)

week46 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_46, volume)
week46 <- mutate(week46, week = 46)
week46 <- week46 |> rename(sales = week_46)

week47 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_47, volume)
week47 <- mutate(week47, week = 47)
week47 <- week47 |> rename(sales = week_47)

week48 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_48, volume)
week48 <- mutate(week48, week = 48)
week48 <- week48 |> rename(sales = week_48)

week49 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_49, volume)
week49 <- mutate(week49, week = 49)
week49 <- week49 |> rename(sales = week_49)

week50 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_50, volume)
week50 <- mutate(week50, week = 50)
week50 <- week50 |> rename(sales = week_50)

week51 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_51, volume)
week51 <- mutate(week51, week = 51)
week51 <- week51 |> rename(sales = week_51)

week52 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_52, volume)
week52 <- mutate(week52, week = 52)
week52 <- week52 |> rename(sales = week_52)

week53 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_53, volume)
week53 <- mutate(week53, week = 53)
week53 <- week53 |> rename(sales = week_53)

total <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, total, volume)
total <- mutate(total, week = total)
total <- total |> rename(sales = total)
```

```{r}
# Combining the newly formed data sets
sales_by_week <- rbind(week1, week2, week3, week4, week5, week6, week7, week8, week9, week10, week11, week12, week13, week14, week15, week16, week17, week18, week19, week20, week21, week22, week23, week24, week25, week26, week27, week28, week29, week30, week31, week32, week33, week34, week35, week36, week37, week38, week39, week40, week41, week42, week43, week44, week45, week46, week47, week48, week49, week50, week51, week52, week53, total)
```


```{r}
average_by_week <- sales_by_week |> group_by(week) |> summarize(average = mean(sales))
```



