---
title: "DATA 205 ABS Data Cleaning and EDA"
author: "Emilio Difilippantonio"
date: "2025-04-07"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(TTR)
library(data.table)
```


```{r}
# Setting working directory
setwd("/Users/emiliodifilippantonio/Desktop/Data Science/Data Science Working Directory")

# Loading in the data set
high <- read_csv("ABS_High_Volume_Weekly.csv")
mid <- read_csv("ABS_Medium_Volume_Weekly.csv")
low <- read_csv("ABS_Low_Volume_Weekly.csv")
```

```{r}
# Renaming the columns
colnames(high) <- c("item_id", "description", "bottles_per_case", "cost_per_bottle", "week_1", "week_2", "week_3", "week_4", "week_5", "week_6", "week_7", "week_8", "week_9", "week_10", "week_11", "week_12", "week_13", "week_14", "week_15", "week_16", "week_17", "week_18", "week_19", "week_20", "week_21", "week_22", "week_23", "week_24", "week_25", "week_26", "week_27", "week_28", "week_29", "week_30", "week_31", "week_32", "week_33", "week_34", "week_35", "week_36",  "week_37", "week_38", "week_39", "week_40", "week_41", "week_42", "week_43", "week_44", "week_45", "week_46", "week_47", "week_48", "week_49", "week_50", "week_51", "week_52", "week_53", "total")

colnames(mid) <- c("item_id", "description", "bottles_per_case", "cost_per_bottle", "week_1", "week_2", "week_3", "week_4", "week_5", "week_6", "week_7", "week_8", "week_9", "week_10", "week_11", "week_12", "week_13", "week_14", "week_15", "week_16", "week_17", "week_18", "week_19", "week_20", "week_21", "week_22", "week_23", "week_24", "week_25", "week_26", "week_27", "week_28", "week_29", "week_30", "week_31", "week_32", "week_33", "week_34", "week_35", "week_36",  "week_37", "week_38", "week_39", "week_40", "week_41", "week_42", "week_43", "week_44", "week_45", "week_46", "week_47", "week_48", "week_49", "week_50", "week_51", "week_52", "week_53", "total")

colnames(low) <- c("item_id", "description", "bottles_per_case", "cost_per_bottle", "week_1", "week_2", "week_3", "week_4", "week_5", "week_6", "week_7", "week_8", "week_9", "week_10", "week_11", "week_12", "week_13", "week_14", "week_15", "week_16", "week_17", "week_18", "week_19", "week_20", "week_21", "week_22", "week_23", "week_24", "week_25", "week_26", "week_27", "week_28", "week_29", "week_30", "week_31", "week_32", "week_33", "week_34", "week_35", "week_36",  "week_37", "week_38", "week_39", "week_40", "week_41", "week_42", "week_43", "week_44", "week_45", "week_46", "week_47", "week_48", "week_49", "week_50", "week_51", "week_52", "week_53", "total")
```

```{r}
# Creating new datasets where the sales are in cases, not bottles
highCase <- mutate(high, week_1 = week_1 / bottles_per_case)
highCase <- mutate(highCase, week_2 = week_2 / bottles_per_case)
highCase <- mutate(highCase, week_3 = week_3 / bottles_per_case)
highCase <- mutate(highCase, week_4 = week_4 / bottles_per_case)
highCase <- mutate(highCase, week_5 = week_5 / bottles_per_case)
highCase <- mutate(highCase, week_6 = week_6 / bottles_per_case)
highCase <- mutate(highCase, week_7 = week_7 / bottles_per_case)
highCase <- mutate(highCase, week_8 = week_8 / bottles_per_case)
highCase <- mutate(highCase, week_9 = week_9 / bottles_per_case)
highCase <- mutate(highCase, week_10 = week_10 / bottles_per_case)
highCase <- mutate(highCase, week_11 = week_11 / bottles_per_case)
highCase <- mutate(highCase, week_12 = week_12 / bottles_per_case)
highCase <- mutate(highCase, week_13 = week_13 / bottles_per_case)
highCase <- mutate(highCase, week_14 = week_14 / bottles_per_case)
highCase <- mutate(highCase, week_15 = week_15 / bottles_per_case)
highCase <- mutate(highCase, week_16 = week_16 / bottles_per_case)
highCase <- mutate(highCase, week_17 = week_17 / bottles_per_case)
highCase <- mutate(highCase, week_18 = week_18 / bottles_per_case)
highCase <- mutate(highCase, week_19 = week_19 / bottles_per_case)
highCase <- mutate(highCase, week_20 = week_20 / bottles_per_case)
highCase <- mutate(highCase, week_21 = week_21 / bottles_per_case)
highCase <- mutate(highCase, week_22 = week_22 / bottles_per_case)
highCase <- mutate(highCase, week_23 = week_23 / bottles_per_case)
highCase <- mutate(highCase, week_24 = week_24 / bottles_per_case)
highCase <- mutate(highCase, week_25 = week_25 / bottles_per_case)
highCase <- mutate(highCase, week_26 = week_26 / bottles_per_case)
highCase <- mutate(highCase, week_27 = week_27 / bottles_per_case)
highCase <- mutate(highCase, week_28 = week_28 / bottles_per_case)
highCase <- mutate(highCase, week_29 = week_29 / bottles_per_case)
highCase <- mutate(highCase, week_30 = week_30 / bottles_per_case)
highCase <- mutate(highCase, week_31 = week_31 / bottles_per_case)
highCase <- mutate(highCase, week_32 = week_32 / bottles_per_case)
highCase <- mutate(highCase, week_33 = week_33 / bottles_per_case)
highCase <- mutate(highCase, week_34 = week_34 / bottles_per_case)
highCase <- mutate(highCase, week_35 = week_35 / bottles_per_case)
highCase <- mutate(highCase, week_36 = week_36 / bottles_per_case)
highCase <- mutate(highCase, week_37 = week_37 / bottles_per_case)
highCase <- mutate(highCase, week_38 = week_38 / bottles_per_case)
highCase <- mutate(highCase, week_39 = week_39 / bottles_per_case)
highCase <- mutate(highCase, week_40 = week_40 / bottles_per_case)
highCase <- mutate(highCase, week_41 = week_41 / bottles_per_case)
highCase <- mutate(highCase, week_42 = week_42 / bottles_per_case)
highCase <- mutate(highCase, week_43 = week_43 / bottles_per_case)
highCase <- mutate(highCase, week_44 = week_44 / bottles_per_case)
highCase <- mutate(highCase, week_45 = week_45 / bottles_per_case)
highCase <- mutate(highCase, week_46 = week_46 / bottles_per_case)
highCase <- mutate(highCase, week_47 = week_47 / bottles_per_case)
highCase <- mutate(highCase, week_48 = week_48 / bottles_per_case)
highCase <- mutate(highCase, week_49 = week_49 / bottles_per_case)
highCase <- mutate(highCase, week_50 = week_50 / bottles_per_case)
highCase <- mutate(highCase, week_51 = week_51 / bottles_per_case)
highCase <- mutate(highCase, week_52 = week_52 / bottles_per_case)
highCase <- mutate(highCase, week_52 = week_52 / bottles_per_case)
highCase <- mutate(highCase, week_53 = week_53 / bottles_per_case)
highCase <- mutate(highCase, total = total / bottles_per_case)

midCase <- mutate(mid, week_1 = week_1 / bottles_per_case)
midCase <- mutate(midCase, week_2 = week_2 / bottles_per_case)
midCase <- mutate(midCase, week_3 = week_3 / bottles_per_case)
midCase <- mutate(midCase, week_4 = week_4 / bottles_per_case)
midCase <- mutate(midCase, week_5 = week_5 / bottles_per_case)
midCase <- mutate(midCase, week_6 = week_6 / bottles_per_case)
midCase <- mutate(midCase, week_7 = week_7 / bottles_per_case)
midCase <- mutate(midCase, week_8 = week_8 / bottles_per_case)
midCase <- mutate(midCase, week_9 = week_9 / bottles_per_case)
midCase <- mutate(midCase, week_10 = week_10 / bottles_per_case)
midCase <- mutate(midCase, week_11 = week_11 / bottles_per_case)
midCase <- mutate(midCase, week_12 = week_12 / bottles_per_case)
midCase <- mutate(midCase, week_13 = week_13 / bottles_per_case)
midCase <- mutate(midCase, week_14 = week_14 / bottles_per_case)
midCase <- mutate(midCase, week_15 = week_15 / bottles_per_case)
midCase <- mutate(midCase, week_16 = week_16 / bottles_per_case)
midCase <- mutate(midCase, week_17 = week_17 / bottles_per_case)
midCase <- mutate(midCase, week_18 = week_18 / bottles_per_case)
midCase <- mutate(midCase, week_19 = week_19 / bottles_per_case)
midCase <- mutate(midCase, week_20 = week_20 / bottles_per_case)
midCase <- mutate(midCase, week_21 = week_21 / bottles_per_case)
midCase <- mutate(midCase, week_22 = week_22 / bottles_per_case)
midCase <- mutate(midCase, week_23 = week_23 / bottles_per_case)
midCase <- mutate(midCase, week_24 = week_24 / bottles_per_case)
midCase <- mutate(midCase, week_25 = week_25 / bottles_per_case)
midCase <- mutate(midCase, week_26 = week_26 / bottles_per_case)
midCase <- mutate(midCase, week_27 = week_27 / bottles_per_case)
midCase <- mutate(midCase, week_28 = week_28 / bottles_per_case)
midCase <- mutate(midCase, week_29 = week_29 / bottles_per_case)
midCase <- mutate(midCase, week_30 = week_30 / bottles_per_case)
midCase <- mutate(midCase, week_31 = week_31 / bottles_per_case)
midCase <- mutate(midCase, week_32 = week_32 / bottles_per_case)
midCase <- mutate(midCase, week_33 = week_33 / bottles_per_case)
midCase <- mutate(midCase, week_34 = week_34 / bottles_per_case)
midCase <- mutate(midCase, week_35 = week_35 / bottles_per_case)
midCase <- mutate(midCase, week_36 = week_36 / bottles_per_case)
midCase <- mutate(midCase, week_37 = week_37 / bottles_per_case)
midCase <- mutate(midCase, week_38 = week_38 / bottles_per_case)
midCase <- mutate(midCase, week_39 = week_39 / bottles_per_case)
midCase <- mutate(midCase, week_40 = week_40 / bottles_per_case)
midCase <- mutate(midCase, week_41 = week_41 / bottles_per_case)
midCase <- mutate(midCase, week_42 = week_42 / bottles_per_case)
midCase <- mutate(midCase, week_43 = week_43 / bottles_per_case)
midCase <- mutate(midCase, week_44 = week_44 / bottles_per_case)
midCase <- mutate(midCase, week_45 = week_45 / bottles_per_case)
midCase <- mutate(midCase, week_46 = week_46 / bottles_per_case)
midCase <- mutate(midCase, week_47 = week_47 / bottles_per_case)
midCase <- mutate(midCase, week_48 = week_48 / bottles_per_case)
midCase <- mutate(midCase, week_49 = week_49 / bottles_per_case)
midCase <- mutate(midCase, week_50 = week_50 / bottles_per_case)
midCase <- mutate(midCase, week_51 = week_51 / bottles_per_case)
midCase <- mutate(midCase, week_52 = week_52 / bottles_per_case)
midCase <- mutate(midCase, week_52 = week_52 / bottles_per_case)
midCase <- mutate(midCase, week_53 = week_53 / bottles_per_case)
midCase <- mutate(midCase, total = total / bottles_per_case)

lowCase <- mutate(low, week_1 = week_1 / bottles_per_case)
lowCase <- mutate(lowCase, week_2 = week_2 / bottles_per_case)
lowCase <- mutate(lowCase, week_3 = week_3 / bottles_per_case)
lowCase <- mutate(lowCase, week_4 = week_4 / bottles_per_case)
lowCase <- mutate(lowCase, week_5 = week_5 / bottles_per_case)
lowCase <- mutate(lowCase, week_6 = week_6 / bottles_per_case)
lowCase <- mutate(lowCase, week_7 = week_7 / bottles_per_case)
lowCase <- mutate(lowCase, week_8 = week_8 / bottles_per_case)
lowCase <- mutate(lowCase, week_9 = week_9 / bottles_per_case)
lowCase <- mutate(lowCase, week_10 = week_10 / bottles_per_case)
lowCase <- mutate(lowCase, week_11 = week_11 / bottles_per_case)
lowCase <- mutate(lowCase, week_12 = week_12 / bottles_per_case)
lowCase <- mutate(lowCase, week_13 = week_13 / bottles_per_case)
lowCase <- mutate(lowCase, week_14 = week_14 / bottles_per_case)
lowCase <- mutate(lowCase, week_15 = week_15 / bottles_per_case)
lowCase <- mutate(lowCase, week_16 = week_16 / bottles_per_case)
lowCase <- mutate(lowCase, week_17 = week_17 / bottles_per_case)
lowCase <- mutate(lowCase, week_18 = week_18 / bottles_per_case)
lowCase <- mutate(lowCase, week_19 = week_19 / bottles_per_case)
lowCase <- mutate(lowCase, week_20 = week_20 / bottles_per_case)
lowCase <- mutate(lowCase, week_21 = week_21 / bottles_per_case)
lowCase <- mutate(lowCase, week_22 = week_22 / bottles_per_case)
lowCase <- mutate(lowCase, week_23 = week_23 / bottles_per_case)
lowCase <- mutate(lowCase, week_24 = week_24 / bottles_per_case)
lowCase <- mutate(lowCase, week_25 = week_25 / bottles_per_case)
lowCase <- mutate(lowCase, week_26 = week_26 / bottles_per_case)
lowCase <- mutate(lowCase, week_27 = week_27 / bottles_per_case)
lowCase <- mutate(lowCase, week_28 = week_28 / bottles_per_case)
lowCase <- mutate(lowCase, week_29 = week_29 / bottles_per_case)
lowCase <- mutate(lowCase, week_30 = week_30 / bottles_per_case)
lowCase <- mutate(lowCase, week_31 = week_31 / bottles_per_case)
lowCase <- mutate(lowCase, week_32 = week_32 / bottles_per_case)
lowCase <- mutate(lowCase, week_33 = week_33 / bottles_per_case)
lowCase <- mutate(lowCase, week_34 = week_34 / bottles_per_case)
lowCase <- mutate(lowCase, week_35 = week_35 / bottles_per_case)
lowCase <- mutate(lowCase, week_36 = week_36 / bottles_per_case)
lowCase <- mutate(lowCase, week_37 = week_37 / bottles_per_case)
lowCase <- mutate(lowCase, week_38 = week_38 / bottles_per_case)
lowCase <- mutate(lowCase, week_39 = week_39 / bottles_per_case)
lowCase <- mutate(lowCase, week_40 = week_40 / bottles_per_case)
lowCase <- mutate(lowCase, week_41 = week_41 / bottles_per_case)
lowCase <- mutate(lowCase, week_42 = week_42 / bottles_per_case)
lowCase <- mutate(lowCase, week_43 = week_43 / bottles_per_case)
lowCase <- mutate(lowCase, week_44 = week_44 / bottles_per_case)
lowCase <- mutate(lowCase, week_45 = week_45 / bottles_per_case)
lowCase <- mutate(lowCase, week_46 = week_46 / bottles_per_case)
lowCase <- mutate(lowCase, week_47 = week_47 / bottles_per_case)
lowCase <- mutate(lowCase, week_48 = week_48 / bottles_per_case)
lowCase <- mutate(lowCase, week_49 = week_49 / bottles_per_case)
lowCase <- mutate(lowCase, week_50 = week_50 / bottles_per_case)
lowCase <- mutate(lowCase, week_51 = week_51 / bottles_per_case)
lowCase <- mutate(lowCase, week_52 = week_52 / bottles_per_case)
lowCase <- mutate(lowCase, week_52 = week_52 / bottles_per_case)
lowCase <- mutate(lowCase, week_53 = week_53 / bottles_per_case)
lowCase <- mutate(lowCase, total = total / bottles_per_case)
```

```{r}
# Adding a variable to indicate store volume (it's redundant in these data set, but when I combine them, it will be useful)
highCase <- mutate(highCase, volume = "high")
midCase <- mutate(midCase, volume = "medium")
lowCase <- mutate(lowCase, volume = "low")
```


```{r}
# Combining all of the data sets
bound <- bind_rows(highCase, midCase, lowCase)

# Making volume a factor and setting the levels
bound$volume <- as_factor(bound$volume)
levels(bound$volume) <- c("high", "medium", "low")
```

The cleaning is finished. Time for EDA.

```{r}
# Plotting total sales of each item across all stores
ggplot(bound, aes(y = total)) +
  geom_boxplot()
```
As we can see, there are many outliers, making it difficult to view and understand the data. Let's remove them and remake the visualization.

```{r}
# Creating the data set without outliers
bound_noOut <- filter(bound, total <= 25)

# Remaking the visualization
ggplot(bound_noOut, aes(y = total)) +
  geom_boxplot() +
  labs(title = "Boxplot of the Number of Cases Sold of Each Product")
```

This graph is much easier to read and tells us that the median number of cases sold of a product in 2024 is about 1, with a heavy rightwards skew that includes some heavy outliers (the ones seen in the previous visualization).

Let's break this data down.

```{r}
# Making a histogram showing sales from each store
ggplot(bound, aes(total)) +
  geom_histogram() +
  facet_wrap(vars(bound$volume), scales = "fixed") +
  labs(
    title = "Frequency of total sales in cases of product\nin 2024 by store volume",
    x = "Store Sales Volume",
    y = "Frequency"
  ) +
  xlim(0, 60) +
  ylim(0, 50)
```

Clearly, something is wrong. I have looked over my code several times but cannot find the mistake.

```{r}
# Creating new data sets for sales in each week
week1 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_1, volume)
week1 <- mutate(week1, week = 1)
week1 <- week1 |> rename(sales = week_1)

week2 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_2, volume)
week2 <- mutate(week2, week = 2)
week2 <- week2 |> rename(sales = week_2)

week3 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_3, volume)
week3 <- mutate(week3, week = 3)
week3 <- week3 |> rename(sales = week_3)

week4 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_4, volume)
week4 <- mutate(week4, week = 4)
week4 <- week4 |> rename(sales = week_4)

week5 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_5, volume)
week5 <- mutate(week5, week = 5)
week5 <- week5 |> rename(sales = week_5)

week6 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_6, volume)
week6 <- mutate(week6, week = 6)
week6 <- week6 |> rename(sales = week_6)

week7 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_7, volume)
week7 <- mutate(week7, week = 7)
week7 <- week7 |> rename(sales = week_7)

week8 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_8, volume)
week8 <- mutate(week8, week = 8)
week8 <- week8 |> rename(sales = week_8)

week9 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_9, volume)
week9 <- mutate(week9, week = 9)
week9 <- week9 |> rename(sales = week_9)

week10 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_10, volume)
week10 <- mutate(week10, week = 10)
week10 <- week10 |> rename(sales = week_10)

week11 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_11, volume)
week11 <- mutate(week11, week = 11)
week11 <- week11 |> rename(sales = week_11)

week12 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_12, volume)
week12 <- mutate(week12, week = 12)
week12 <- week12 |> rename(sales = week_12)

week13 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_13, volume)
week13 <- mutate(week13, week = 13)
week13 <- week13 |> rename(sales = week_13)

week14 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_14, volume)
week14 <- mutate(week14, week = 14)
week14 <- week14 |> rename(sales = week_14)

week15 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_15, volume)
week15 <- mutate(week15, week = 15)
week15 <- week15 |> rename(sales = week_15)

week16 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_16, volume)
week16 <- mutate(week16, week = 16)
week16 <- week16 |> rename(sales = week_16)

week17 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_17, volume)
week17 <- mutate(week17, week = 17)
week17 <- week17 |> rename(sales = week_17)

week18 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_18, volume)
week18 <- mutate(week18, week = 18)
week18 <- week18 |> rename(sales = week_18)

week19 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_19, volume)
week19 <- mutate(week19, week = 19)
week19 <- week19 |> rename(sales = week_19)

week20 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_20, volume)
week20 <- mutate(week20, week = 20)
week20 <- week20 |> rename(sales = week_20)

week21 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_21, volume)
week21 <- mutate(week21, week = 21)
week21 <- week21 |> rename(sales = week_21)

week22 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_22, volume)
week22 <- mutate(week22, week = 22)
week22 <- week22 |> rename(sales = week_22)

week23 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_23, volume)
week23 <- mutate(week23, week = 23)
week23 <- week23 |> rename(sales = week_23)

week24 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_24, volume)
week24 <- mutate(week24, week = 24)
week24 <- week24 |> rename(sales = week_24)

week25 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_25, volume)
week25 <- mutate(week25, week = 25)
week25 <- week25 |> rename(sales = week_25)

week26 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_26, volume)
week26 <- mutate(week26, week = 26)
week26 <- week26 |> rename(sales = week_26)

week27 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_27, volume)
week27 <- mutate(week27, week = 27)
week27 <- week27 |> rename(sales = week_27)

week28 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_28, volume)
week28 <- mutate(week28, week = 28)
week28 <- week28 |> rename(sales = week_28)

week29 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_29, volume)
week29 <- mutate(week29, week = 29)
week29 <- week29 |> rename(sales = week_29)

week30 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_30, volume)
week30 <- mutate(week30, week = 30)
week30 <- week30 |> rename(sales = week_30)

week31 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_31, volume)
week31 <- mutate(week31, week = 31)
week31 <- week31 |> rename(sales = week_31)

week32 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_32, volume)
week32 <- mutate(week32, week = 32)
week32 <- week32 |> rename(sales = week_32)

week33 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_33, volume)
week33 <- mutate(week33, week = 33)
week33 <- week33 |> rename(sales = week_33)

week34 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_34, volume)
week34 <- mutate(week34, week = 34)
week34 <- week34 |> rename(sales = week_34)

week35 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_35, volume)
week35 <- mutate(week35, week = 35)
week35 <- week35 |> rename(sales = week_35)

week36 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_36, volume)
week36 <- mutate(week36, week = 36)
week36 <- week36 |> rename(sales = week_36)

week37 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_37, volume)
week37 <- mutate(week37, week = 37)
week37 <- week37 |> rename(sales = week_37)

week38 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_38, volume)
week38 <- mutate(week38, week = 38)
week38 <- week38 |> rename(sales = week_38)

week39 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_39, volume)
week39 <- mutate(week39, week = 39)
week39 <- week39 |> rename(sales = week_39)

week40 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_40, volume)
week40 <- mutate(week40, week = 40)
week40 <- week40 |> rename(sales = week_40)

week41 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_41, volume)
week41 <- mutate(week41, week = 41)
week41 <- week41 |> rename(sales = week_41)

week42 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_42, volume)
week42 <- mutate(week42, week = 42)
week42 <- week42 |> rename(sales = week_42)

week43 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_43, volume)
week43 <- mutate(week43, week = 43)
week43 <- week43 |> rename(sales = week_43)

week44 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_44, volume)
week44 <- mutate(week44, week = 44)
week44 <- week44 |> rename(sales = week_44)

week45 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_45, volume)
week45 <- mutate(week45, week = 45)
week45 <- week45 |> rename(sales = week_45)

week46 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_46, volume)
week46 <- mutate(week46, week = 46)
week46 <- week46 |> rename(sales = week_46)

week47 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_47, volume)
week47 <- mutate(week47, week = 47)
week47 <- week47 |> rename(sales = week_47)

week48 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_48, volume)
week48 <- mutate(week48, week = 48)
week48 <- week48 |> rename(sales = week_48)

week49 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_49, volume)
week49 <- mutate(week49, week = 49)
week49 <- week49 |> rename(sales = week_49)

week50 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_50, volume)
week50 <- mutate(week50, week = 50)
week50 <- week50 |> rename(sales = week_50)

week51 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_51, volume)
week51 <- mutate(week51, week = 51)
week51 <- week51 |> rename(sales = week_51)

week52 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_52, volume)
week52 <- mutate(week52, week = 52)
week52 <- week52 |> rename(sales = week_52)

week53 <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, week_53, volume)
week53 <- mutate(week53, week = 53)
week53 <- week53 |> rename(sales = week_53)

total <- bound |> select(item_id, description, bottles_per_case, cost_per_bottle, total, volume)
total <- mutate(total, week = 0)
total <- total |> rename(sales = total)
```

```{r}
# Combining the newly formed data sets
sales_by_week <- rbind(week1, week2, week3, week4, week5, week6, week7, week8, week9, week10, week11, week12, week13, week14, week15, week16, week17, week18, week19, week20, week21, week22, week23, week24, week25, week26, week27, week28, week29, week30, week31, week32, week33, week34, week35, week36, week37, week38, week39, week40, week41, week42, week43, week44, week45, week46, week47, week48, week49, week50, week51, week52, week53, total)
```

```{r}
# Finding the average number of cases of product sold each week by store volume
average_by_week <- sales_by_week |> group_by(week, volume) |> summarize(average = mean(sales))

# Making the data set without the total
average_by_week_no_total <- average_by_week[4:162,]
```

```{r}
# Graphing the data set we just created
ggplot(average_by_week_no_total, aes(x = week, y = average)) +
  geom_line() +
  facet_wrap(average_by_week_no_total$volume) +
  labs(title = "Average Number of Cases Sold for\nEach Product by Week and Store Volume",
       x = "Week",
       y = "Average Number of Cases Sold\nfor Each Product")
```

The sales seem to spike at points, and at the end of the year, they plummet for a week, but other than that, the data seems pretty stable. It should be usable for an algorithm.

Let's visualize the data together.

```{r}
# Creating the same graph, but using a color key instead of facet wrapping
ggplot(average_by_week_no_total, aes(x = week, y = average, color = volume)) +
  geom_line()
```

Once again, the data seems pretty stable.

```{r}
# Creating a new data set
just_sales <- bound[, 5:57]

# Combining the columns of the data set
just_sales_condensed <- c(just_sales$week_1, just_sales$week_2, just_sales$week_3, just_sales$week_4, just_sales$week_5, just_sales$week_6, just_sales$week_7, just_sales$week_8, just_sales$week_9, just_sales$week_10, just_sales$week_11, just_sales$week_12, just_sales$week_13, just_sales$week_14, just_sales$week_15, just_sales$week_16, just_sales$week_17, just_sales$week_18, just_sales$week_19, just_sales$week_20, just_sales$week_21, just_sales$week_22, just_sales$week_23, just_sales$week_24, just_sales$week_25, just_sales$week_26, just_sales$week_27, just_sales$week_28, just_sales$week_29, just_sales$week_30, just_sales$week_31, just_sales$week_32, just_sales$week_33, just_sales$week_34, just_sales$week_35, just_sales$week_36, just_sales$week_37, just_sales$week_38, just_sales$week_39, just_sales$week_40, just_sales$week_41, just_sales$week_42, just_sales$week_43, just_sales$week_44, just_sales$week_45, just_sales$week_46, just_sales$week_47, just_sales$week_48, just_sales$week_49, just_sales$week_50, just_sales$week_51, just_sales$week_52, just_sales$week_53)
```

```{r}
# Transposing sales to run it through the EMA function
wide_sales <- transpose(just_sales)
wide_sales <- data.frame(wide_sales)
```

```{r}
# Calculating the EMA of every column
exp_mov_avg <- wide_sales

for (i in 1:ncol(wide_sales)) {
  obj <- EMA(wide_sales[, i], 3)
  exp_mov_avg[, i] <- obj
}

# Transposing the output
exp_mov_avg <- transpose(exp_mov_avg)
```

```{r}
# Recreating the bound data set
EMA_plus <- bound

# Replacing the weekly sales with the moving average
EMA_plus[, 5:57] <- exp_mov_avg
```

I will find the 5- and 7- week exponential moving averages for the sales, the 3-, 5-, and 7-week unweighted moving averages, and the 3-, 5-, and 7-week weighted moving averages for a weighting that I will create.

I will then test these to determine which most closely align with actual sales, but I will also favor algorithms that are fairly steady, as high responsiveness to recent changes may be negative.

I may use different algorithms for different sales volumes. For example, I may look at the standard deviation of weekly sales for a product and use that to determine how long of a time frame to use for the moving average. More volatile sales will warrant longer time frames to ensure that the predicted sales is relatively close to average sales, while less volatile sales will allow for shorter time frames that are more responsive to trends in sales without the risk of excessively low or high reorder quantities.